---
title: "Welcome to My Blog"
description: |
 
author:
  - name: Abdoul ISSA BIDA 
    url: https://abdoulblog.netlify.app
date: 06-18-2021
preview: preview.png
categories: 
  - R 
  - Python
output:
  distill::distill_article:
    self_contained: false
bibliography : ../articles.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
optspars <- list(align="center")
library(twitterwidget)
library(emo) # For display emoticon https://github.com/hadley/emo
# For emoticon name https://github.com/ikatyang/emoji-cheat-sheet#face-smiling 

# Learn more about creating blogs with Distill at:
# https://rstudio.github.io/distill/blog.html

```

I  started learning `R` a couple months ago, because I spend a lot time on Twitter and was always amazed by  all the great graphics  made with this statistical programming language. 
First of all, I followed essentially some great sport Data Analysts like [Owen Phillips](https://twitter.com/owenlhjphillips) who post great charts about NBA Players & Community Stats. 

<blockquote>
<p>Some Owen's Tweets</p>
<div>
```{r}
twitterwidget('1377974728233734148', optspars, height = 650)
```
</div><br>

<div>
```{r}
twitterwidget('1405137683467456513', optspars, height = 575)
```
</div><br>

-- Owen Pihllips(\@owenlhjphillips)
</blockquote>
<br>

And as things progress, I started following more and more people from R Community and particularly those who contribute to the `Tidytuesday` weekly Data Visualization Challenge.

As, my passion keeps growing, I started learning R typically with short tutorial like those amazing ones from [Cédric Scherer](https://www.cedricscherer.com/2019/08/05/a-ggplot2-tutorial-for-beautiful-plotting-in-r/?s=09) or [Thomas Mock](https://themockup.blog/) but also with some `bookdown` particularly the bible  for the beginners and the aspiring data scientists R for Data Science [@Wickham2017R].


On May 5, 2020, I made my first contribution for the **Tidytuesday** Challenge. I wasn't expecting a lot of likes but what happened was just magical.

<blockquote>
The dataset was about Water Acces Points and come from [WPDX](https://www.waterpointdata.org/). 
My analysis of the data wasn't the adequate one and my lines plot was even less, but my intention was principally to give birth to a presentable plot with my beginner knowledge.

```{r twitter_status}
twitterwidget('1389976276765716488', optspars, height = 450)
```
-- <cite>Abdoul Madjid(\@issa_madjid)</cite>
</blockquote>
<br>
I received a ton of compliments and advices for that meme lines plot, what acted like a boost for my little ego <span style ="font-size: 1.25rem">`r emo::ji("sweat_smile")`</span>. So from that initial post, I have decided, despite my professional life schedule:

- to be a  weekly contributor to the **TidyTuesday Challenge** 
- to try to progress from the feedback I received from the Community
- and to build a blog with [{distill}](https://rstudio.github.io/distill/) which is used to build scientific and technical writing and native blog with **R Markdown**



<div style = "margin-top: 20px;text-align:center;font-weight:bold; font-size : 2.5rem !important;">So Here, We go. </div>

## Acknowledgement {.appendix}
A big thank to all the amazing contributors to the R community.
