---
title: "Welcome to My Blog"
description: |
 
author:
  - name: Abdoul ISSA BIDA 
    url: https://example.com/norajones
date: 06-18-2021
preview: preview.png
categories: 
  - R 
  - Python
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(twitterwidget)
# Learn more about creating blogs with Distill at:
# https://rstudio.github.io/distill/blog.html

```

I  started learning `R` a couple months ago, because I spend a lot time on Twitter and was always amazed by  all the great graphics  made with this statistical programming langage. 
Fist of all, I followed essentially some great sport Data Analysts like [Owen Phillips](https://twitter.com/owenlhjphillips) who post great charts about NBA Players & Community Stats. 

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Ha! This is an excerpt from our abstract: <br><br>Our preliminary analysis found that only 2.4% of the images contained a text description entered by the tweet author compared to 84% which were described by default as &quot;Image&quot; 😬<br><br>Full abstract available at <a href="https://t.co/nqn9VFgWkK">https://t.co/nqn9VFgWkK</a></p>&mdash; Silvia Canelón (@spcanelon) <a href="https://twitter.com/spcanelon/status/1375238625437351939?ref_src=twsrc%5Etfw">March 26, 2021</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

And as things progress, I started following people from R Community and particulary those who contribute to the `Tidytuesday` weeekly Data Vizualisation Challenge. 

As, my passion keep growing, I started learning R typpically with short tutorial like the Amazing one [Cédric Scherer](https://www.cedricscherer.com/2019/08/05/a-ggplot2-tutorial-for-beautiful-plotting-in-r/?s=09) but also with some `bookdown` particulary the bible  for the beginners and the aspiring data scientists [R for Data Science](https://r4ds.had.co.nz/introduction.html) by **Hadley Wicham** and **Garett Grolemund**.


On May 5th, I make my first submission to the `Tidytuesday` Challenge. I didn't wait for a lot likes but what happened was just magical. 

<blockquote>
```{r twitter_status}
optspars <- list(align="center")
twitterwidget('1389976276765716488', optspars)
```
</blockquote>
<br>

I received a ton of compliments  and advices for a  simple lines plot.