---
title: "Welcome to My Blog"
description: |
 
author:
  - name: Abdoul ISSA BIDA 
    url: https://example.com/norajones
date: 06-18-2021
preview: preview.png
categories: 
  - R 
  - Python
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
optspars <- list(align="center")
library(twitterwidget)
# Learn more about creating blogs with Distill at:
# https://rstudio.github.io/distill/blog.html

```

I  started learning `R` a couple months ago, because I spend a lot time on Twitter and was always amazed by  all the great graphics  made with this statistical programming langage. 
Fist of all, I followed essentially some great sport Data Analysts like [Owen Phillips](https://twitter.com/owenlhjphillips) who post great charts about NBA Players & Community Stats. 

<blockquote>
<p>Some Owen's Tweets</p>
```{r}
twitterwidget('1377974728233734148', optspars, height = 700)
```

-- Owen Pihllips(@owenlhjphillips)
</blockquote>
<br><br>

And as things progress, I started following people from R Community and particulary those who contribute to the `Tidytuesday` weeekly Data Vizualisation Challenge. 

As, my passion keep growing, I started learning R typpically with short tutorial like the Amazing one [Cédric Scherer](https://www.cedricscherer.com/2019/08/05/a-ggplot2-tutorial-for-beautiful-plotting-in-r/?s=09) but also with some `bookdown` particulary the bible  for the beginners and the aspiring data scientists [R for Data Science](https://r4ds.had.co.nz/introduction.html) by **Hadley Wicham** and **Garett Grolemund**.


On May 5th, I make my first submission to the `Tidytuesday` Challenge. I didn't wait for a lot likes but what happened was just magical. 

<blockquote>
The dataset was about Water Acces Points and come from [WPDX](https://www.waterpointdata.org/). 
My analysis of the data wasn't the adequate one and my lines plot was even less but  my intention was principally 
to give birth to a presentable plot with my beginner knowledge. 

```{r twitter_status}
twitterwidget('1389976276765716488', optspars, height = 450)
```
-- <cite>Abdoul Madjid(@issa_madjid)</cite>
</blockquote>
<br>
I received a ton of compliments  and advices for a  simple lines plot.